Binning Strategies and Related Loss for Large Data

### 2015-02-28 Paper.Rnw
reference for Hermann grid illusion

As alternatives, Figure~\ref{fig:scatter-alpha} (d-e) contains examples of a hexagonally binned scatterplot with frequency encoded as color (d) \hh{XXX the bubble plots already got mention above XXX} and a ``bubble plot" (referred to as a modified scatterplot) with frequency encoded as point size (e). The hexagonal tiles and the modified scatterplot are more effective at displaying the shape of the joint density and preserving outliers than any of the scatterplots shown in Figure~\ref{fig:scatter-alpha} (a-c). The binned scatterplot is less prone to the Hermann-grid illusion \hh{needs a reference} 
than the bubble plot, particularly for binned data, where bin centers usually fall on a grid.

>>>>

As alternatives, Figure~\ref{fig:scatter-alpha} (d-e) contains examples of a hexagonally binned scatterplot with frequency encoded as color (d) \hh{XXX the bubble plots already got mention above XXX} and a ``bubble plot" (referred to as a modified scatterplot) with frequency encoded as point size (e). The hexagonal tiles and the modified scatterplot are more effective at displaying the shape of the joint density and preserving outliers than any of the scatterplots shown in Figure~\ref{fig:scatter-alpha} (a-c). The binned scatterplot is less prone to the Hermann-grid illusion \citep{hermann:1870} 
than the bubble plot, particularly for binned data, where bin centers usually fall on a grid.
